A simulation-based assessment of the relation between Stone Age sites and relative sea-level change along the Norwegian Skagerrak coast

### 2022-11-10 analysis/paper/paper.Rmd
Only using the DTM tile for Hegna Vest 1 in paper.rmd, instead of the entire DTM

```{r load_dtm, include = FALSE}
# This chunk tries to the load the edited DTM. Due to the file sizes involved,
# this is distributed as tiles which have to be merged by running 00dtm_prep.R

# Digital terrain model
# dtm <- rast(here("analysis/data/derived_data/dtm10.tif"))
dtm <- rast("/home/isak/phd/eaa_presentation/dtm10/dtm10.tif")

>>>>

```{r load_dtm, include = FALSE}
# Load DTM tile for the example site Hegna Vest 1
dtm <- rast(here("analysis/data/raw_data/tiled_dtm/output210d2773e79a4907927a671b18efd762-004-009.tif"))
